Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining

### 2015-08-31 2_relatedwork/relatedwork.tex
no message

>>>>

 Within the process mining framework, there are various different process mining algorithms proposed which have the same aim of discovering underlying processes. Considering the underlying approaches undertaken, algorithms can be grouped as $\alpha$-algorithms \cite{van2004workflow,de2004process}, inductive approaches \cite{herbst1998integrating,herbst2000dealing}, hierarchical clustering \cite{greco2005mining}, genetic approaches \cite{van2005genetic,esgin2010hybrid}, and heuristic approaches \cite{esgin2009hybrid}. Considering the scope of this study; process discovery operations are undertaken with inductive methods which is a robust, repeatable and mature set of approaches.
